### 2016-12-02 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor text changes to CAF report; resolved plot.py flag issue

In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two-story structure.  Two different fuel packages were utilized, the difference between the furniture fuel package used for experiments 13 and 14, and the furniture and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.

@@

The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling. The three couches were aligned along the west wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic Figure~\ref{fig:furniture_2story}. In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE), and polypropylene (PP).

@@

In June 2015, two stacks of pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding. Each stack had 10 pallets and an approximate mass of 175~kg (386~lb). Hay from bales averaging a mass of 12~kg (26~lb) was added for ignition purposes. The specific locations of the fuel load's contents can be found in the dimensioned schematic Figure~\ref{fig:pallet_furniture_2story}.

@@

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used. The data show that thermocouples from Array 2 (TC\_A2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (TC\_A1 and TC\_A3). This is the result of Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 also exhibits some amount of suppression agent impact. Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions. As a result, it remained dry and seems to provide the best representation of the gas cooling.

\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent. Shown are Tests 2, 3, and 4 from Table~\ref{tab:Gas_Cooling_Descriptions}}
	\label{fig:gas_cooling_sub1}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAF as the Suppression Agent. Shown are Tests 52, 53, and 54 from Table~\ref{tab:Gas_Cooling_Descriptions}}
	\label{fig:gas_cooling_sub5}
\end{figure}

@@

There were seven suppression tests conducted in the two-story, purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling. Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the ground floor and available ventilation was through the ground floor double doors and the door on the south side of the second story of the structure. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the basement double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted. In all cases, ventilation was provided through open basement doors and a door on the first floor.

@@

The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two thermocouple arrays in the fire room. Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression. In Figure~\ref{fig:fs_a10}, only tests Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.

>>>>

In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the two-story structure.  Two different fuel packages located on the ground level were utilized throughout the experiments: experiments 13 and 14 used a fuel package composed primarily of furniture, and experiments 15 through 20 used the same fuel package with an addition of two stacks of wood pallets.

@@

The fuel load for experiments 13 and 14 consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling. The three couches were aligned along the west wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic Figure~\ref{fig:furniture_2story}. In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE), and polypropylene (PP).

@@

For experiments 15 through 20, two stacks of wood pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding. Each stack had 10 pallets and an approximate mass of 175~kg (386~lb). Hay from bales with an average a mass of 12~kg (26~lb) was added for ignition purposes. The specific locations of the fuel load's contents can be found in the dimensioned schematic Figure~\ref{fig:pallet_furniture_2story}.

@@

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used. The data show that thermocouples from Array 2 (``TC~A2'' in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (``TC~A1'' and ``TC~A3''). This is the result of Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 also exhibits some amount of suppression agent impact. Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions. As a result, it remained dry and seems to provide the best representation of the gas cooling.

\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
	\caption{Time Series of Thermocouple Data from Three Arrays in Gas Cooling Room with Water as the Suppression Agent. Shown are Tests 2, 3, and 4 from Table~\ref{tab:Gas_Cooling_Descriptions}}
	\label{fig:gas_cooling_sub1}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
	\caption{Time Series of Thermocouple Data from Three Arrays in Gas Cooling Room with CAF as the Suppression Agent. Shown are Tests 52, 53, and 54 from Table~\ref{tab:Gas_Cooling_Descriptions}}
	\label{fig:gas_cooling_sub5}
\end{figure}

@@

There were seven suppression tests conducted in the two-story, purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling. Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the ground floor and available ventilation was through the ground floor double doors and the south exterior door on the second story of the structure. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the ground level double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.

@@

The impact of water and CAF during fire suppression can again be analyzed by comparing the temperature differences during the suppression interval at the various thermocouple arrays throughout the structure. Figure~\ref{fig:fs_a10} shows the temperature difference comparison at array A10 for CAF and water after suppression. In Figure~\ref{fig:fs_a10}, the tests Water~7 \& 8 are compared to CAF~7 \& 8a because they all contained similar experimental configurations.
